Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-13 paper.qmd
Added script to make the model with tSNE

<!--UMAP applied for Two curvy data-->
```{r}
#| label: umap-two-curvy
tsne_two_curvy <- read_rds(file = "data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_tsne_perplexity_30.rds")

@@

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 23

>>>>

<!--tSNE applied for Two curvy data-->
```{r}
#| label: tsne-two-curvy
tsne_two_curvy <- read_rds(file = "data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_tsne_perplexity_30.rds")

@@

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 27
